ray

### 2022-03-20 outputs/paper/ray.Rmd
graphs

```{r}
class_data <- raw_data %>% select(c(hlthmntl, class)) %>% filter(!is.na(class), !is.na(hlthmntl)) %>%
  mutate(class_d = case_when(
    class == 1 ~ "lower",
    class == 2 ~ "working",
    class == 3 ~ "lower middle",
    class == 4 ~ "middle",
    class == 5 ~ "upper middle",
    class == 6 ~ "upper",

@@

income_data %>% ggplot(aes(x=hlthmntl, fill=income)) +
  geom_histogram(aes(y = ..density..), position = 'identity', alpha=0.3)

@@

@@

>>>>

```{r}
class_data <- raw_data %>% select(c(hlthmntl, class1)) %>% filter(!is.na(class1), !is.na(hlthmntl)) %>%
  mutate(class_d = case_when(
    class1 == 1 ~ "lower",
    class1 == 2 ~ "working",
    class1 == 3 ~ "lower middle",
    class1 == 4 ~ "middle",
    class1 == 5 ~ "upper middle",
    class1 == 6 ~ "upper",

@@

income_data %>% ggplot(aes(x=hlthmntl, fill=income)) +
  geom_histogram(aes(y = ..density..), position = 'dodge', alpha=1)

@@

  )) %>%
  mutate(mntl_poor = case_when(1
    hlthmntl <= 3 ~ 'Good',
    hlthmntl >= 4 ~ 'Not Good',
  ))

@@

# Older ppl % in upper class
```{r}
old_upper <- raw_data %>% select(c(age, class1))

length(which(old_upper$age > 50 & old_upper$class1 == 6)) / length(which(old_upper$class1 == 6))
```
